Refinements for open pNets

### 2021-07-12 2021-Refinement/paper/refinementarticle.tex
first rough version of an abstract .

>>>>

Establishing equivalences and refinement relations between programs is an important mean for 
verifying the correctness of programs, by formaly proving the relation between a specification and an implementation, 
proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
behaviors of a modified program simulate those of to the source one.

In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
behavioral models for communicationg systems. Open automata may have "holes" modeling elements of their
context, and can be composed by instanciation of the holes. This allows for a compositional approach for
verification of their behavior, essential to address proofs about large realistic systems.

We define several varriants of refinement between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata. We also discuss
the relations between these refinements and the existence of deadlocks.
We iluustrate these notions on several simple use-cases.
